Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-20 paper/reply.tex
new reply

The referee expressed 5 major points of concern. Some of them were due
to unclearly written sections, other made reference to issues with the
observational data and choices to perform the comparison against the
simulated data.\\

In this new version we respond to all these concerns. We have
clarified the text where it was needed and performed new tests on the
data. We have also corrected an error in the computation of the
angular correlation function, strenghtening our conclusions. Therefore
we resubmit this draft to be considered for publication in the MNRAS.\\

We wish to emphasize that our paper uses a new method in the context
of the study of LAE galaxies. Correspondingly, the results are novel
with respect to the already published literature.\\

In what follows we reply to each one of the major points raised by the
referee. The comments by the referee are in boldface. Our reply
follows to each of these comments.\\

@@

  We agree with the referee that the two statistical tests should be
  performed on the same data set. Unfortunately neither the galaxy catalog
  nor the ACF from Yamada et al. 2012 are available. We contacted
  Dr. Yamada asking for information about the ACF, but we didn't get
  any reply.

  The currrent version of the draft features a comparison with the ACF
  from a survey with an average number density from Hayashino et al
  2004.

  On the other hand, Using a small field as Ouchi's for our analysis
  is not feasible, given that our method is based on the analysis of
  the surface density \emph{distribution among different}
  fields. Having the distribution data is central to discard a large
  fraction of models (Section 3.3).

@@

  As the referee highlights, we have found a new set of acceptable
  parameters for the escape fraction than those that have been
  previously claimed by the literature.

  However, we do not find a clear evidence for a degeneracy between
  the occupation fraction $f_{\rm occ}$ and the mass range $\Delta
  M$. There is, however, a clear degeneracy between the minium halo
  mass $M_{\rm min}$ and the occupation fraction.

  The reason for that trend is easy to understand. In LCDM the halo
  number density $n$ is verysensitive to the mass. The dependency is
  roughly $n\propto  M_{h}^{-1}$. Therefore, at a fixed minimum halo
  mass, increasing the mass range by 1.0 dex barely raises the number
  density by  
  $0.10$. Increasing the mass range by 2.0 dex  raises the number
  density by $0.11$. This explains that we cannot find any clear
  dependence between $\Delta M$ and the $f_{\rm occ}$. On the other
  hand, decreasing the minium mass by 1.0 dex would increas the number
  density by a factor of {\bf $10$} (!). Requiring that models with
  small values for the minium mass to have a small occupation
  fraction.

  This trend is clearly seen on the right panel of Figure 3,4 and
  6. This implies that exploring very low escape fractions values of
  $0.01$ would require the exploration of halo masses aroud the range
  of $10^{9}$ Msun or   below, which is lower than the minimum halo
  masss of $10^{9.5}$ Msun   that is confidently resolved in the
  simulation.

@@

We agree with the referee that a comparison of a $\sim 5 $ overdensity
with an average field would not be fair. Therefore we have removed
that constraint from the results in the new version of the paper. Now
we only include the ACF comparison against the results of an average
density field from Ouchi 2008.

Related to this point we have added the left panel in Figure 1 and
subsection 2.2 to discuss the adequacy of including SSA22 as an
observational benchmark in the number density tests.

@@

We have corrected all the mistakes where we meant occupation
fraction but wrote escape fraction. We have alsoremoved the discussion
comparing our results to escape fraction estimates, in spite of the
effort of other authors to link these two different quantities.

@@

As we mentioned before in the Reply to Major Point 2, tiny values of
0.001 can only produce reasonable models for very low mass halos. This
is due to the contraint on the number density. An occupation fraction
of 0.001 requires models with a minimum mass on the order of $M_{\rm
  min}=10^{9}$ solar masses, which is well below the mass resolution
of the simulation we use. This comment has been added to the paper.

>>>>

The referee expressed 5 major points of concern. Some of them were due
to unclear written sections, other made reference to issues with the
choice of observational data used to compare against the mocks.\\

In this new version we respond to all these concerns. We have
clarified the text where it was needed and performed new tests on the
data. We have also corrected a small error in the presentation of the
results for the angular correlation function. All these modifications
and improvements strengthen the conclusions already
presented. Therefore we resubmit this draft to be considered for
publication in the MNRAS.\\

We wish to emphasize that our paper presents a new method in the context
of the study of LAE at high redshift. Correspondingly, the results are
novel with respect to the already published literature.\\

In what follows we reply to each one of the major points raised by the
referee. The comments by the referee are in boldface. Our reply
follows to each one of the comments.\\

@@

  We follow the referee's suggestion and perform the ACF analysis
  using Ouchi's data.

  We made this choice because neither the galaxy catalog
  nor the ACF from Yamada et al. 2012 are available. We contacted
  Dr. Yamada asking for information about the ACF, but we didn't get
  any reply.

@@

  As the referee highlights, we have found a new set of acceptable
  parameters for the escape fraction $f_{\rm occ}>0.1$. We stress that
  an occupation fraction of $0.1$ is on the upper end of the accepted
  values by Gawiser et al. 2007. At the same time all the mass ranges
  we find acceptable are within the wide mass range already published
  by observers. All this seems to be good news rather a caveat.

  The reason for a narrow mass range $\Delta M$ does not
  seem to be a consequence from the constraint on the occupation
  fraction to be larger than $0.1$. We do not find a clear evidence
  for a degeneracy between the occupation fraction $f_{\rm occ}$ and
  the mass range $\Delta M$. However we would appreciaty a pointer to
  any reference presenting evidence for the opossite.

  However, there is a clear degeneracy between the minimum halo mass
  $M_{\rm min}$ and the occupation fraction.This trend is clearly
  seen on the right panel of Figure 3,4 and 6. This implies that
  exploring very low escape fractions values of the range $0.01$ would
  require building mock catalogs with a minimum mass around the range
  $10^{9.5}$Msun or below which is precisely the minimum halo mass of
  that is resolved in the simulation. This intrinsic limitation on the
  range of values that can be explored is now explicit in the paper.

  All in all, we consider this result for a narrow
  mass range $\Delta M<1.0$ (in many cases $\Delta M<0.5$) a novel
  one, since it has not been mentioned in the literature before.

@@

We agree with the referee that a comparison of a $\sim 5 $ overdensity
with an average field would not be fair. Therefore we have removed
the comparison from the ACF in the SSA22 field in the new version of
the paper. We only include the ACF comparison against the results of
an average density field from Ouchi 2008.

Related to this point we have added the left panel in Figure 1 and
subsection 2.2.1 to discuss the adequacy of including SSA22 as an
observational benchmark in the number density tests.

In that subsection we emphasize that it is only one of the subfields
in SSA22 that represents at 3-$\sigma$ overdensity. The whole field
has an average density compared to other blank fields.

@@

We have corrected all the mistakes where we meant occupation
fraction but wrote escape fraction. We have also removed the discussion
comparing our results to escape fraction estimates, in spite of the
effort of other authors to link these two different quantities.

@@

As we mentioned before in the reply to Major Point 2, tiny values of
0.001 can only produce reasonable models for very low mass halos. This
is due to the constraint on the number density distribution. An
occupation fraction of 0.001 requires models with a minimum mass on
the order of $M_{\rm min}=10^{9}$ solar masses, which is well below
the mass resolution of the simulation we use. This comment has been
added to the paper.
